\sysfull

### 2018-08-07 paper/asplos19/intro.tex
revised and ready

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-coalesced-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by using a novel approach called \emph{dynamic group privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys keeps memory consistent through \emph{memory virtualization} optimized for bulk accesses to task-shared data with high locality.

@@

The rest of this paper is organized as follows. Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. The dynamic group privatization is explained in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's evaluation methodology and results. Section~\ref{sec:related_work} positions \sys in the context of related work and Section~\ref{sec:conclusions} concludes and discusses future work.

>>>>

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-coalesced-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by using a novel approach called \emph{dynamic page privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys keeps memory consistent through \emph{memory virtualization} optimized for bulk accesses to task-shared data with high locality.

@@

The rest of this paper is organized as follows. Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. The dynamic page privatization is explained in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's evaluation methodology and results. Section~\ref{sec:related_work} positions \sys in the context of related work and Section~\ref{sec:conclusions} concludes and discusses future work.
